### 2012-06-14 web/12.su.reg/exams/exam5.su.12.alt.tex
Exam 5 alt, Exam 6, exam solutions, and assignment 6.

\documentclass[11pt]{article}

%% ------------------------------------------------------------------
%% SOLUTIONS:
\def\thel{\noindent\rule{2.5cm}{.5pt}}
\long\def\begsol#1 #2\endsol{#1}
%\def\begsol#1{\thel {\bf Solution} \thel}\def\endsol{\relax}
%%uncomment the above line to get the solutions printed

@@

\vfill
\centerline{\Large CS 2510 Exam 4 -- Summer 2012}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{45}
\begin{problem}
An association list is a way of representing an association between
values.  For example, you might you use an association list to
associate students with their grades, or battleships with their
position, or bank account numbers with their account balances.

The representation of an association list is much like a typical list,
except that every ``cons'' has \emph{two} elements and the rest of the
list.  One element is a ``key'', the other is its association.

Here is a data definition for association lists parameterized over the
types of keys and their values:

\begin{verbatim}
interface Assoc<K,V> {}

class EmptyAssoc<K,V> implements Assoc<K,V> {}

class ConsAssoc<K,V> implements Assoc<K,V> {
  K key;
  V val;
  Assoc<K,V> rest;
  ConsAssoc(K key, V val, Assoc<K,V> rest) {
    this.key = key;
    this.val = val;
    this.rest = rest;
  }
}
\end{verbatim}

\begin{enumerate}
\item Develop the visitor pattern for association lists.
\item Design an implementation of an association list visitor that
  looks up the (first) value associated to a given key.  If the key is
  not in the list, the visitor shoud throw an exception.
\item Using the double dispatch approach, design a {\tt same} method
  that determines if this association list is structurally equal to a
  given association list.
\end{enumerate}
\end{problem}
\newpage
\ 
\newpage
\ 
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath}
%% ------------------------------------------------------------------
%% SOLUTIONS:
\def\thel{\noindent\rule{2.5cm}{.5pt}}
\long\def\begsol#1 #2\endsol{#1}
%\def\begsol#1{\thel {\bf Solution} \thel}\def\endsol{\relax}
%%uncomment the above line to get the solutions printed

@@

\vfill
\centerline{\Large CS 2510 Exam 5 (Alternate) -- Summer 2012}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{45}
\begin{problem}
Develop an implementation of {\tt Comparator<Square>} that orders
squares by their area in such a way that the smaller the area, the
\emph{greater} the square is considered.  So for example, there is no
square greater than the one with width $= 0$ and height $= 0$.

You may rely on the following definition of {\tt Square}:

\begin{verbatim}
// Represents a square with given height and width.
class Square {
  Integer width;
  Integer height;
  Square(Integer width, Integer height) {
    this.width = width;
    this.height = height;
  }
}
\end{verbatim}
\end{problem}

\newpage
\begin{problem}
Design a method:
\begin{center}
{\tt <T> Boolean noSameNeighbors(ArrayList<T> ls, Comparator<T> c)}
\end{center}
that determines if the given array list has no adjacent elements
(i.e.~neighboring elements) that are considered of equal size
according to the given comparator.
\end{problem}
\newpage
\begin{problem}
Design a method:
\begin{verbatim}
<A> Comparator<ArrayList<A>> dict(Comparator<A> ca)
\end{verbatim}
that consumes a comparator for {\tt A}s and and produces a comparator
for array lists of {\tt A}s that is the \emph{dictionary order} (aka
\emph{alphabetic order}).

In other words, given an ordering on individual elements, produce an
ordering on \emph{lists of} elements that corresponds to the ordering
used in dictionaries.  A dictionary uses an ordering on individual
letters (single elements) to make an ordering on strings of letters
(lists of elements) so that ``abc'' $<$ ``abcd'', ``abc'' $<$ ``adc'',
``abc'' $>$ ``ab'', and ``abc'' $=$ ``abc'', etc.
\end{problem}
\ 
\newpage
\ 
\newpage
\ 
\end{document}
